### 2025-11-04 modern-portfolio-theory.qmd
20251104 - fixes

In @fig-teamPortfolio2, we depict the combined mean of projected fantasy points for a Quarterback/Running Back/Wide Receiver combination as a function of the standard deviation of their projected fantasy points across sources.

>>>>

In @fig-teamPortfolio2, we depict the combined mean of historical fantasy points for a Quarterback/Running Back/Wide Receiver combination as a function of the historical standard deviation of their fantasy points across games.
